---
title: "Analysis and Comparison"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(tidyverse)
library(knitr)
```

```{r}
optimized <- read.csv("optimized_l_stars.csv")
paired <- read.csv("paired_l_stars.csv")
randomized <- read.csv("randomized_l_stars.csv")
exact_scores <- read.csv("exact_scores.csv")
```

### Approximation ratios

calculate the approximation ratios and actual ratios for k= 3, 4, 5
```{r}
optimized.exact <- merge(optimized, exact_scores, by=c("k", "round")) %>% 
  mutate(approx_ratio=2-l/k, actual_ratio=score/exact_score)

paired.exact <- merge(paired, exact_scores, by=c("k", "round")) %>% 
  mutate(approx_ratio=2-l/k, actual_ratio=score/exact_score)
  
randomized.exact <- merge(randomized, exact_scores, by=c("k", "round")) %>% 
  mutate(approx_ratio=2-l/(2*k), actual_ratio=score/exact_score)
```

check if actual ratio is smaller than the approximation ratio for all test cases
```{r}
all(optimized.exact$actual_ratio <= optimized.exact$approx_ratio)
all(paired.exact$actual_ratio <= paired.exact$approx_ratio)
all(randomized.exact$actual_ratio <= randomized.exact$approx_ratio)
```



### Optimized l-stars

Compute an average time and score for each distinct pair of k and l:
```{r}
optimized <- optimized %>% 
  group_by(k, l) %>% 
  mutate(avg_time = mean(time), avg_score = mean(score)) %>% 
  ungroup()
```

A table summarizes the average score for each pair of k and l:
```{r}
optimized %>% 
  group_by(k, l) %>% 
  summarise(average_score=mean(score)) %>% 
  spread(l, average_score) %>% 
  kable()
```

A table summarizes the average running time(s) for each pair of k and l:
```{r}
optimized %>% 
  group_by(k, l) %>% 
  summarise(average_time=mean(time)) %>% 
  spread(l, average_time) %>% 
  kable()
```

Running time against the number of sequences k
```{r}
optimized %>% 
  mutate(l=as.factor(l)) %>% 
  ggplot(aes(k, time)) + 
  geom_jitter(aes(color=l)) + 
  geom_line(aes(k, avg_time, color=l)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```

SP score against the number of sequences k
```{r}
optimized %>% 
  mutate(l=as.factor(l)) %>% 
  ggplot(aes(k, score)) + 
  geom_jitter(aes(color=l)) + 
  geom_line(aes(k, avg_score, color=l)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```


### (2l-1)-stars
Compute an average time and score for each distinct pair of k and l:
```{r}
paired <- paired %>% 
  group_by(k, l) %>% 
  mutate(avg_time = mean(time), avg_score = mean(score)) %>% 
  ungroup()
```

A table summarizes the average score for each pair of k and l:
```{r}
paired %>% 
  group_by(k, l) %>% 
  summarise(average_score=mean(score)) %>% 
  spread(l, average_score) %>% 
  kable()
```

A table summarizes the average running time(s) for each pair of k and l:
```{r}
paired %>% 
  group_by(k, l) %>% 
  summarise(average_time=mean(time)) %>% 
  spread(l, average_time) %>% 
  kable()
```

Running time against the number of sequences k
```{r}
paired %>% 
  mutate(l=as.factor(l)) %>% 
  ggplot(aes(k, time)) + 
  geom_jitter(aes(color=l)) + 
  geom_line(aes(k, avg_time, color=l)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```

SP score against the number of sequences k
```{r}
paired %>% 
  mutate(l=as.factor(l)) %>% 
  ggplot(aes(k, score)) + 
  geom_jitter(aes(color=l)) + 
  geom_line(aes(k, avg_score, color=l)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```

### Randomized l-stars

Compute an average time and score for each distinct pair of k and l:
```{r}
randomized <- randomized %>% 
  group_by(k, l, eps) %>% 
  mutate(avg_time = mean(time), avg_score = mean(score)) %>% 
  ungroup()
```

A table summarizes the average score for each pair of k and l:
```{r}
randomized %>% 
  group_by(k, l) %>% 
  summarise(average_score=mean(score)) %>% 
  spread(l, average_score) %>% 
  kable()
```

A table summarizes the average running time(s) for each pair of k and l:
```{r}
randomized %>% 
  group_by(k, l) %>% 
  summarise(average_time=mean(time)) %>% 
  spread(l, average_time) %>% 
  kable()
```

Running time against the number of sequences k (eps=0.1)
```{r}
randomized %>% 
  filter(eps==0.1) %>% 
  mutate(l=as.factor(l)) %>% 
  ggplot(aes(k, time)) + 
  geom_jitter(aes(color=l)) + 
  geom_line(aes(k, avg_time, color=l)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```

SP score against the number of sequences k
```{r}
randomized %>% 
  filter(eps==0.1) %>% 
  mutate(l=as.factor(l)) %>% 
  ggplot(aes(k, score)) + 
  geom_jitter(aes(color=l)) + 
  geom_line(aes(k, avg_score, color=l)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```

When l = 4, running time against the number of sequences k for different epsilon
```{r}
randomized %>% 
  filter(l==4) %>% 
  mutate(eps=as.factor(eps)) %>% 
  ggplot(aes(k, time)) + 
  geom_jitter(aes(color=eps)) + 
  geom_line(aes(k, avg_time, color=eps)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```
When l = 4, score against the number of sequences k for different epsilon
```{r}
randomized %>% 
  filter(l==4) %>% 
  mutate(eps=as.factor(eps)) %>% 
  ggplot(aes(k, score)) + 
  geom_jitter(aes(color=eps)) + 
  geom_line(aes(k, avg_score, color=eps)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```

### comparison

#### fixed approximation ratio
For a fixed theoretical approximation ratio = 2-l/k
- optimized: l=2
- (2l-1)-stars: l=2
- randomized: l=4, eps=0.1

```{r}
optimized.2 <- optimized %>% 
  filter(l==2) %>% 
  mutate(algo="optimized")

paired.2 <- paired %>% 
  filter(l==2) %>% 
  mutate(algo="paired")

randomized.2 <- randomized %>% 
  filter(l==4, eps==0.1) %>% 
  select(-eps) %>% 
  mutate(algo="randomized")

df <- rbind(optimized.2, paired.2, randomized.2)
```

Running time against the number of sequences k
```{r}
df %>% 
  ggplot(aes(k, time)) + 
  geom_jitter(aes(color=algo)) + 
  geom_line(aes(k, avg_time, color=algo)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```


SP score against the number of sequences k
```{r}
df %>% 
  ggplot(aes(k, score)) + 
  geom_jitter(aes(color=algo)) + 
  geom_line(aes(k, avg_score, color=algo)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```

#### fixed clique size
For a fixed clique size l
- optimized: l=3
- (2l-1)-stars: l=2
- randomized: l=3, eps=0.1

```{r}
optimized.3 <- optimized %>% 
  filter(l==3) %>% 
  mutate(algo="optimized")

paired.3 <- paired %>% 
  filter(l==2) %>% 
  mutate(algo="paired")

randomized.3 <- randomized %>% 
  filter(l==3, eps==0.1) %>% 
  select(-eps) %>% 
  mutate(algo="randomized")

df.3 <- rbind(optimized.3, paired.3, randomized.3)
```

Running time against the number of sequences k
```{r}
df.3 %>% 
  ggplot(aes(k, time)) + 
  geom_jitter(aes(color=algo)) + 
  geom_line(aes(k, avg_time, color=algo)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```


SP score against the number of sequences k
```{r}
df.3 %>% 
  ggplot(aes(k, score)) + 
  geom_jitter(aes(color=algo)) + 
  geom_line(aes(k, avg_score, color=algo)) +
  scale_x_continuous(breaks=c(3,5,7,9,11,13))
```